%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer (Java Developer)} % Job title
    {Fusemachines} % Organization
    {Kathmandu, Nepal} % Location
    {Aug. 2016 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented RESTful API server for finding Vehicle compatibility with OBD device.}
        \item {Data import and export to database.}  
        \item {Unit and integration tests.}        
        \item {Reviewing and resolving issues and software bugs.}   
        \item {Documentation.}        
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer (DevOps Engineer)} % Job title
    {Fusemachines} % Organization
    {Kathmandu, Nepal} % Location
    {Jan. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provisioned an easily managable Amazon AWS infrastructure utilizing IaC(Infrastructure as Code) tools like Ansible.}
        \item {Built fully automated CI/CD pipelines on Jenkins for containerized applications using Docker.}
        \item {Customize Dockerfile of Jupyterhub notebook (Python IDE on cloud) to allow multi-user collaboration.}
        \item {Automate deployment of Linux applications and system
configurations.}
        \item {Collaborating with developers to make sure new environments meet requirements and conform to best practices.}
        \item {Deployed a centralized monitoring environment(Grafana, InfluxDB, CollectD) which gather system metrics as well as docker run-time metrics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Quality Assurance Engineer and Tester} % Job title
    {Xensam} % Organization
    {Stockholm, Sweden} % Location
    {Aug. 2019 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designing a test strategy/test plan.}
        \item {Test software solutions with Sentry during product development.}
        \item {Reporting software defects and work with development team to resolve them.}
        \item {Documenting and communicating findings and software quality improvements.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Remote Software Consultant (Quality Assurance Engineer)} % Job title
    {Xensam} % Organization
    {Stockholm, Sweden} % Location
    {Mar. 2020 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working as QA including writing unit tests, manual testing}
        \item {Spinning up testing environments with HyperV, KVM, Active Directory Domain controller}
        \item {Test data management with open source AD-lab generator}
      \end{cvitems}
    }

%---------------------------------------------------------
 
%---------------------------------------------------------
\end{cventries}
